```{r}
library(tidyverse)
library(readxl)
library(readr)
```

```{r}
x <- read_excel('cv_data.xlsx')
```

```{r}
Sys.setenv(OPENAI_API_KEY = "")
```

```{r}
description_cols <- c(
  "description_1",
  "description_2",
  "description_3",
  "description_4",
  "description_5"
)

updated_entries <- alter_dataframe_text(
  df = cv$entries_data,
  instruction = "Rewrite the descriptions so they sound more corporate, polished, and professional. Do not invent experience, tools, or metrics. Keep the meaning faithful.",
  text_columns = description_cols,
  model = "gpt-4.1-mini",
  api_key = ""
)
```

```{r}
library(gptr)
library(httr2)
library(jsonlite)
library(dplyr)

alter_dataframe_text <- function(
  df,
  instruction,
  text_columns = NULL,
  model = "gpt-4.1-mini",
  api_key
) {
  if (missing(api_key) || is.null(api_key) || api_key == "") {
    stop("You must provide a valid OpenAI API key.")
  }

  if (missing(instruction) || is.null(instruction) || instruction == "") {
    stop("You must provide an instruction string.")
  }

  if (!is.data.frame(df)) {
    stop("`df` must be a dataframe.")
  }

  # Default: alter all character columns
  if (is.null(text_columns)) {
    text_columns <- names(df)[vapply(df, is.character, logical(1))]
  }

  if (length(text_columns) == 0) {
    stop("No text columns found to alter.")
  }

  missing_cols <- setdiff(text_columns, names(df))
  if (length(missing_cols) > 0) {
    stop(
      paste(
        "These columns are not in the dataframe:",
        paste(missing_cols, collapse = ", ")
      )
    )
  }

  # Build payload with row id
  payload_df <- df %>%
    mutate(.row_id = row_number()) %>%
    select(.row_id, all_of(text_columns))

  df_json <- jsonlite::toJSON(
    payload_df,
    dataframe = "rows",
    auto_unbox = TRUE,
    pretty = TRUE,
    na = "null"
  )

  prompt_text <- paste0(
    "You will receive a JSON array representing rows from a dataframe.\n\n",
    "Your task is to modify ONLY these columns: ",
    paste(text_columns, collapse = ", "),
    ".\n\n",
    "User instruction:\n",
    instruction,
    "\n\n",
    "Rules:\n",
    "- Preserve the number of rows exactly.\n",
    "- Preserve .row_id exactly.\n",
    "- Return exactly one object per input row.\n",
    "- Return ONLY raw JSON.\n",
    "- Do not include markdown.\n",
    "- Do not include explanations.\n",
    "- Do not add or remove columns.\n",
    "- Keep null values as null.\n",
    "- Only change the requested text content.\n\n",
    "Return a JSON array of objects with exactly these keys:\n",
    paste(c(".row_id", text_columns), collapse = ", "),
    "\n\n",
    "Input data:\n",
    df_json
  )

  req_body <- list(
    model = model,
    input = list(
      list(
        role = "user",
        content = list(
          list(
            type = "input_text",
            text = prompt_text
          )
        )
      )
    )
  )

  safe_openai_post <- function(req) {
    resp <- req_perform(req)
    status <- resp_status(resp)
    body <- resp_body_string(resp)

    if (status >= 400) {
      cat("HTTP status:", status, "\n")
      cat(body, "\n")
      stop("OpenAI request failed. See body above.")
    }

    resp
  }

  extract_output_text <- function(resp_json) {
    if (!is.null(resp_json$output_text)) {
      return(resp_json$output_text)
    }

    if (!is.null(resp_json$output) &&
        length(resp_json$output) > 0 &&
        !is.null(resp_json$output[[1]]$content) &&
        length(resp_json$output[[1]]$content) > 0 &&
        !is.null(resp_json$output[[1]]$content[[1]]$text)) {
      return(resp_json$output[[1]]$content[[1]]$text)
    }

    stop("Could not extract text output from the API response.")
  }

  clean_json_array <- function(x) {
    x <- gsub("```json", "", x, fixed = TRUE)
    x <- gsub("```", "", x, fixed = TRUE)
    x <- trimws(x)

    start_pos <- regexpr("\\[", x)
    end_pos <- max(gregexpr("\\]", x)[[1]])

    if (start_pos[1] == -1 || end_pos[1] == -1) {
      stop("Could not find a JSON array in the model output.")
    }

    substr(x, start_pos[1], end_pos[1])
  }

  req <- request("https://api.openai.com/v1/responses") %>%
    req_headers(
      Authorization = paste("Bearer", api_key),
      `Content-Type` = "application/json"
    ) %>%
    req_body_json(req_body, auto_unbox = TRUE)

  resp <- safe_openai_post(req)
  resp_json <- resp_body_json(resp)

  out_text <- extract_output_text(resp_json)
  cleaned <- clean_json_array(out_text)

  rewritten <- jsonlite::fromJSON(cleaned, simplifyDataFrame = TRUE)

  if (!is.data.frame(rewritten)) {
    stop("Parsed output is not a dataframe.")
  }

  expected_cols <- c(".row_id", text_columns)
  missing_returned <- setdiff(expected_cols, names(rewritten))
  if (length(missing_returned) > 0) {
    stop(
      paste(
        "The model output is missing these expected columns:",
        paste(missing_returned, collapse = ", ")
      )
    )
  }

  if (nrow(rewritten) != nrow(df)) {
    stop(
      paste0(
        "Row count mismatch. Input rows: ", nrow(df),
        "; returned rows: ", nrow(rewritten), "."
      )
    )
  }

  rewritten <- rewritten %>%
    arrange(.row_id)

  result <- df %>%
    mutate(.row_id = row_number()) %>%
    left_join(
      rewritten %>% select(all_of(expected_cols)),
      by = ".row_id",
      suffix = c("", "__new")
    )

  for (col in text_columns) {
    new_col <- paste0(col, "__new")
    result[[col]] <- result[[new_col]]
    result[[new_col]] <- NULL
  }

  result$.row_id <- NULL

  result
}


# Example 1
#response1 <- get_response(user_input = "How to calculate the bonforoni corrected p values?")
```

```{r}

response2 <- get_response(user_input = paste0("Based on this data.frame in R: \n\n",
                                               dataframe_to_text(cv$entries_data),
                                               "\n\n can you rewrite the descriptions for each role in recent professional experience to something more corporate oriented? give me a dataframe as output with the updated text blocks"))
```

```{r}
library(httr2)
library(jsonlite)
library(dplyr)

rewrite_entries <- function(df, api_key, model = "gpt-4.1-mini") {
  library(httr2)
  library(jsonlite)
  library(dplyr)
  library(tidyr)

  required_cols <- c(
    "title", "institution", "loc", "start", "end",
    "description_1", "description_2", "description_3",
    "description_4", "description_5"
  )

  missing_cols <- setdiff(required_cols, names(df))
  if (length(missing_cols) > 0) {
    stop(
      paste(
        "The dataframe is missing these required columns:",
        paste(missing_cols, collapse = ", ")
      )
    )
  }

  # Build a temporary payload for the model
  payload_df <- df %>%
    mutate(
      row_id = row_number(),
      timeline = paste(
        ifelse(is.na(start), "", as.character(start)),
        ifelse(is.na(end), "", as.character(end)),
        sep = " - "
      ),
      timeline = trimws(timeline),
      description_bullets = paste(
        dplyr::coalesce(as.character(description_1), ""),
        dplyr::coalesce(as.character(description_2), ""),
        dplyr::coalesce(as.character(description_3), ""),
        dplyr::coalesce(as.character(description_4), ""),
        dplyr::coalesce(as.character(description_5), ""),
        sep = "\n"
      ),
      description_bullets = gsub("\n+", "\n", description_bullets),
      description_bullets = gsub("(^\n+|\n+$)", "", description_bullets)
    ) %>%
    select(row_id, title, institution, loc, timeline, description_bullets)

  # Convert dataframe to JSON safely
  df_json <- jsonlite::toJSON(
    payload_df,
    dataframe = "rows",
    auto_unbox = TRUE,
    pretty = TRUE,
    na = "null"
  )

  prompt_text <- paste0(
    "You will receive a JSON array representing rows from a CV dataframe.\n",
    "Rewrite ONLY the field `description_bullets` for each row so it sounds more corporate, polished, and professional.\n",
    "Keep the meaning faithful to the original text.\n",
    "Do not invent tools, metrics, achievements, responsibilities, or experience that are not already present.\n",
    "Preserve the number of bullet points whenever possible.\n",
    "Return ONLY valid JSON as an array of objects with exactly these fields:\n",
    "row_id, description_bullets\n\n",
    "IMPORTANT:\n",
    "- Keep bullet points separated by newline characters.\n",
    "- Do not include markdown.\n",
    "- Do not include any extra fields.\n\n",
    "Input data:\n",
    df_json
  )

  req_body <- list(
    model = model,
    input = list(
      list(
        role = "user",
        content = list(
          list(
            type = "input_text",
            text = prompt_text
          )
        )
      )
    ),
    text = list(
      format = list(
        type = "json_schema",
        name = "rewritten_cv_rows",
        schema = list(
          type = "array",
          items = list(
            type = "object",
            properties = list(
              row_id = list(type = "integer"),
              description_bullets = list(type = "string")
            ),
            required = list("row_id", "description_bullets"),
            additionalProperties = FALSE
          )
        )
      )
    )
  )

  resp <- request("https://api.openai.com/v1/responses") %>%
    req_headers(
      Authorization = paste("Bearer", api_key),
      `Content-Type` = "application/json"
    ) %>%
    req_body_json(req_body, auto_unbox = TRUE) %>%
    req_perform()

  resp_json <- resp_body_json(resp)

  # Try to extract the returned text robustly
  out_text <- NULL

  if (!is.null(resp_json$output_text)) {
    out_text <- resp_json$output_text
  } else if (!is.null(resp_json$output[[1]]$content[[1]]$text)) {
    out_text <- resp_json$output[[1]]$content[[1]]$text
  } else {
    stop("Could not extract text output from the API response.")
  }

  rewritten <- jsonlite::fromJSON(out_text)

  if (!all(c("row_id", "description_bullets") %in% names(rewritten))) {
    stop("The model output did not contain the expected fields: row_id, description_bullets")
  }

  # Join rewritten text back
  df_out <- payload_df %>%
    select(row_id) %>%
    left_join(rewritten, by = "row_id") %>%
    mutate(
      description_bullets = gsub("\r\n", "\n", description_bullets),
      description_bullets = gsub("\n+", "\n", description_bullets),
      description_bullets = gsub("(^\n+|\n+$)", "", description_bullets)
    ) %>%
    tidyr::separate(
      description_bullets,
      into = c(
        "description_1",
        "description_2",
        "description_3",
        "description_4",
        "description_5"
      ),
      sep = "\n",
      fill = "right",
      extra = "merge",
      remove = FALSE
    )

  # Replace original description columns with rewritten ones
  result <- df %>%
    mutate(
      description_1 = df_out$description_1,
      description_2 = df_out$description_2,
      description_3 = df_out$description_3,
      description_4 = df_out$description_4,
      description_5 = df_out$description_5
    )

  return(result)
}
```


```{r}
data_location <- 'https://docs.google.com/spreadsheets/d/1mIF3aDXQJOPzfPJqOmbdY4QMsa_asKxsjb7AieAB7xA/edit?usp=sharing'

cv <- list()

cv$entries_data <- googlesheets4::read_sheet(data_location, sheet = "entries", skip = 1, col_types = "c")
cv$skills       <- googlesheets4::read_sheet(data_location, sheet = "language_skills", skip = 1, col_types = "c")
cv$text_blocks  <- googlesheets4::read_sheet(data_location, sheet = "text_blocks", skip = 1, col_types = "c")
cv$contact_info <- googlesheets4::read_sheet(data_location, sheet = "contact_info", skip = 1, col_types = "c")
```

Now I need to edit the content of these sections using the llm prompts and rebuild a sheet and upload it.

```{r}
cv$entries_data
```