---
title: "Lucas Moraes's CV"
author: Lucas Moraes
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
  data_location:
    value: ""
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results = 'asis',
  echo = FALSE
)

library(magrittr)

source("cv_printing_functions.r")

CV <- create_CV_object(
  data_location = params$data_location,
  pdf_mode = params$pdf_mode,
  skip_rows = 0
)
```

```{r}
if (params$pdf_mode) {
  cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

Main
================================================================================

Lucas Moraes {#title}
--------------------------------------------------------------------------------

<p align="justify">

```{r}
CV %<>% print_text_block("intro")
```

</p>

<br>

Relevant professional experience {data-icon=suitcase}
--------------------------------------------------------------------------------

::: aside

**Education & Contact**

<i class="fa fa-envelope"></i> mSC & bSC in Genetics and Molecular Biology

<i class="fa fa-envelope"></i> moraessaur@gmail.com

<i class="fa fa-github"></i> [GitHub: `@`moraessaur](https://github.com/moraessaur)

<i class="fab fa-linkedin-in"></i> [LinkedIn](https://www.linkedin.com/in/lucas-moraes-msc-78944a32/)

<i class="fas fa-award"></i> **Fluent English**

:::

```{r}
CV %<>% print_section("recent_professional_experience")
```

\newpage

::: aside

<i class="fa-solid fa-globe"></i> Able to bridge business, data science, and engineering needs effectively

<i class="fa-solid fa-chart-simple"></i></i> Expertise in Statistics, Machine Learning, and stakeholder management

<i class="fa-solid fa-sitemap"></i> Experienced collaborating closely with MLOps teams on production systems

<i class="fa-solid fa-cubes"></i> Active involvement in deploying, monitoring, and maintaining ML models in production


:::

Skills & Stack {#about-me data-icon=laptop-code}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section(
  "skills_stack",
  glue_template = "
<div class='skills-stack-entry'>

<div class='skills-stack-title'>{title}</div>

{description_bullets}

</div>
\n\n"
)
```